---
title: "Untitled"
output: html_document
---
#(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above. You're encouraged to use a "wide" structure similar to how the information appears above, so that you can practice tidying and transformations as described below.
```{r}
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
```
#(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy and transform your data.
```{r}
table <- read.csv("https://raw.githubusercontent.com/Zchen116/assignment-2/master/flights.csv", header = TRUE, stringsAsFactors = FALSE)
```
#Remove the blank row that contains NAs
```{r}
table <- table[!apply(is.na(table) | table == "", 1, all),] 
table
```
#rename column
```{r}
names(table)[1] <- "Airline"
names(table)[2] <- "Arrival_Status"
table
```
#Fill in the missing values
```{r}
table$Airline[2] <- table$Airline[1]
table$Airline[4] <- table$Airline[3]
table
```
#Combine City and Flights in one data table
```{r}
airlines <- gather(table, "City", "Flights", 3:7)
airlines
```
#Combine Arrival Status and Flights in one data table
```{r}
airlines_2 <- spread(airlines, Arrival_Status, Flights)
airlines_2
```
#(3) Perform analysis to compare the arrival delays for the two airlines.
```{r}
Compare_City <- airlines_2 %>%
  group_by(City, Airline) %>%
  summarize(delay_ratio = sum(delayed) / (sum(delayed) + sum(`on time`)))
Compare_City %>% spread(Airline, delay_ratio)
```
#From cities delay comparison, we see that ALASKA's delay ratio is smaller than AM WEST's in every city.
```{r}
Compare_airlines <- airlines_2 %>%
  group_by(Airline) %>% 
  summarize(total_delayed = sum(delayed), total_flights = sum(delayed) + sum(`on time`), delay_ratio = sum(delayed) / (sum(delayed) + sum(`on time`))) 
Compare_airlines
```
#From airlines delay comparison on total flights and delay ratio, we see that AM WEST had more flights than ALASKA (about twice as more as ALASKA) with a smaller delay ratio.



