---
title: "Untitled"
output: html_document
---
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
  
dataset3 <-"https://raw.githubusercontent.com/Zchen116/assignment-2/master/infant_mortality_rate_2019.csv"
dataset3_total<-read.csv(dataset3, header = TRUE, stringsAsFactors = FALSE)
head(dataset3_total)
```
#create another data frame include populations on every twenty years
```{r}
dt_sel <- select(dataset3_total, c(1,2,25,45))
dt_sel
```
#combine all of the years into one column and the number of people into another.
```{r}
#This is the point where I combine all of the years into one column and the number of people into another. 
names(dt_sel)
dt_sel_tidy <- dt_sel %>% gather("Year_month", "Population", 3:4)
dt_sel_tidy %>% arrange(Country.Name,Year_month,Population) 
head(dt_sel_tidy)
```

```{r}
country_list <- dt_sel_tidy %>% 
  arrange(Population) %>% 
  select(Country.Name)
country_list  = country_list[1:10,]
country_list  
dt_sel_tidy10<- dt_sel_tidy %>%  filter(Country.Name %in% country_list)
head(dt_sel_tidy10,3)
```
#Analysis: 
```{r}
ggplot(dt_sel_tidy10, aes(x = Year_month , y = as.numeric(Population), group = Country.Name, colour = Country.Name)) +
  geom_line() +
  geom_point() +
  theme_bw() +
  ylab("Polulation") +
  xlab("Year_month") +
  ggtitle("Countries with highest number of deaths of children under five") +
  ylab("Population") +
  theme(plot.title = element_text(lineheight = .8))